Allele frequencies and positions

### 2021-01-05 R/Analysis_v0.5_snp_allele_frequencies_and_other_info.Rmd
Start greenup mash analysis using weather covariances matrices as U_hyp

---
title: "Allele frequencies and positions"
author: "Alice MacQueen"
date: "11/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bigsnpr)
library(cowplot)
#library(maps)
#library(ggmap)
#library(ggrepel)
#usa <- map_data("usa")
library(switchgrassGWAS)

>>>>

---
title: "Allele frequencies and positions"
author: "Alice MacQueen"
date: "11/18/2020"
output: html_document
---
# TRIAL script
# -----------------------------
NB: Trial to get other metadata for mash SNPs and to plot that data as colors in the mashhattan to add information to these plots.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bigsnpr)
library(cowplot)
#library(maps)
#library(ggmap)
#library(ggrepel)
#usa <- map_data("usa")
library(switchgrassGWAS)
